---
title: Trends in patient characteristics and outcomes of cancer patients admitted
  to the ICU of a tertiary teaching hospital in the U.S.
author: "Christopher M. Sauer"
date: "May 07, 2018"
output:
  word_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(sjmisc)
library(plyr)
library(Hmisc)
library(epitools)
library(sjPlot)
library(MIMICbook)
library(devtools)
library(dplyr)
library(ggplot2)
library(tableone)
library(MASS)

setwd("C:/Users/chris/OneDrive/MPH/ICU- Trends survival cancer/Newest dataset")
onco = read.table("dataset_trend_cancer_clinical_processed.txt", sep="\t", header=TRUE) 
angus= read.table("dataset_angus_sepsis_clinical.txt")
colnames(angus)=c("SUBJECT_ID" , "HADM_ID" , "ICUSTAY_ID", "SEPSIS")

onco2 <- onco %>% group_by(SUBJECT_ID , HADM_ID , ICUSTAY_ID , AGE_ADMISSION , GENDER, RACE, MARITAL_STATUS, ELIXHAUSER_VANWALRAVEN, ELIXHAUSER_SID29, ELIXHAUSER_SID30, VASOPRESSORS_DURATION_MINUTES, VENTILATION_DURATION_MINUTES, OASIS_SCORE, APSIII_SCORE,ICU_TYPE ,RRT ,DNR_ADMISSION, DNR_ANY, CMO_ADMISSION, CMO_ANY, SOFA_SCORE ,SAPS_SCORE ,MORTALITY_ICU, MORTALITY_TIME, LOS_ICU ,LOS_HOSPITAL ,SOLID_TUMOR ,METASTATIC_CANCER, LYMPHOMA) %>% summarise(ORALMAL = sum(ORALMAL), GIMAL = sum(GIMAL), RESPMAL=sum(RESPMAL), CONNMAL = sum(CONNMAL), GUMAL = sum(GUMAL), OTHERMAL = sum(OTHERMAL), TRUELYMPHOMA=sum(TRUELYMPHOMA), OTHERHEMMAL=sum(OTHERHEMMAL), LEUKEMIA=sum(LEUKEMIA))

load (file= "records_groups.RData")
comb<-merge(x=onco2,y=records_groups,fix.by=c("SUBJECT_ID_x", "HADM_ID_x",all.x=TRUE))

reason= read.csv("reason admission.csv")
comb <-left_join(comb, reason, by=c("SUBJECT_ID", "HADM_ID"))

comb <- comb[comb$GROUP>=2,]
comb <- comb[comb$GROUP<=11,]
comb$GROUP<-comb$GROUP+2000

comb <- comb %>%  mutate(OTHERMAL = ifelse(OTHERMAL >= 1, "Yes", ifelse (OTHERMAL == 0, "No", NA)))
comb <- comb %>%  mutate(GIMAL = ifelse(GIMAL >= 1, "Yes", ifelse (GIMAL == 0, "No", NA)))
comb <- comb %>%  mutate(RESPMAL = ifelse(RESPMAL >= 1, "Yes", ifelse (RESPMAL == 0, "No", NA)))
comb <- comb %>%  mutate(CONNMAL = ifelse(CONNMAL >= 1, "Yes", ifelse (CONNMAL == 0, "No", NA)))
comb <- comb %>%  mutate(GUMAL = ifelse(GUMAL >= 1, "Yes", ifelse (GUMAL == 0, "No", NA)))
comb <- comb %>%  mutate(ORALMAL = ifelse(ORALMAL >= 1, "Yes", ifelse (ORALMAL == 0, "No", NA)))
comb <- comb %>%  mutate(TRUELYMPHOMA = ifelse(TRUELYMPHOMA >= 1, "Yes", ifelse (TRUELYMPHOMA == 0, "No", NA)))
comb <- comb %>%  mutate(OTHERHEMMAL = ifelse(OTHERHEMMAL >= 1, "Yes", ifelse (OTHERHEMMAL == 0, "No", NA)))
comb <- comb %>%  mutate(LEUKEMIA = ifelse(LEUKEMIA >= 1, "Yes", ifelse (LEUKEMIA == 0, "No", NA)))
comb <- comb %>%  mutate(OTHERMAL = ifelse(OTHERMAL== "Yes" & GIMAL=="No" & RESPMAL=="No" & CONNMAL=="No" &GUMAL=="No" &ORALMAL=="No", "Yes", "No"))
comb <- comb %>%  mutate(OTHERHEMMAL = ifelse(OTHERHEMMAL== "Yes" & LEUKEMIA=="No" & TRUELYMPHOMA=="No", "Yes", "No"))

comb <- comb %>%  mutate(race2= ifelse(comb$RACE == "WHITE" | comb$RACE== "WHITE - RUSSIAN" | comb$RACE == "WHITE - EASTERN EUROPEAN", "White", "Non-White"))

comb <- comb %>%  mutate(m28.flg = ifelse(is.na(MORTALITY_TIME), "0",
                                          ifelse(MORTALITY_TIME<= 28, "1", "0")))
comb <- comb %>%  mutate(m1y.flg = ifelse(is.na(MORTALITY_TIME), "0",
                                      ifelse(MORTALITY_TIME<= 365, "1", "0")))

comb$VASOPRESSORS_DURATION_MINUTES<- as.numeric(comb$VASOPRESSORS_DURATION_MINUTES)
comb <- comb %>%  mutate(vaso.flg = ifelse(is.na(VASOPRESSORS_DURATION_MINUTES), "0", 
                                           ifelse(VASOPRESSORS_DURATION_MINUTES>= -999, "1", "0")))


comb$VENTILATION_DURATION_MINUTES<- as.numeric(comb$VENTILATION_DURATION_MINUTES)
comb <- comb %>%  mutate(vent.flg = ifelse(is.na(VENTILATION_DURATION_MINUTES), "0", 
                                           ifelse(VENTILATION_DURATION_MINUTES>= -999, "1", "0")))

comb <- comb %>%  mutate(onc.flg= ifelse(comb$GUMAL== "Yes" | comb$GIMAL== "Yes" | comb$RESPMAL== "Yes" | comb$CONNMAL== "Yes" | comb$OTHERMAL== "Yes" | comb$ORALMAL== "Yes", "1", "0"))
comb <- comb %>%  mutate(hem.flg= ifelse(comb$TRUELYMPHOMA== "Yes" | comb$LEUKEMIA== "Yes" | comb$OTHERHEMMAL== "Yes", "1", "0"))
comb <- comb %>%  mutate(mal.flg= ifelse(hem.flg=="1"| onc.flg =="1", "1","0"))

comb <- comb %>%  mutate(sofa.cut = ifelse(SOFA_SCORE <= 5, "low", ifelse (SOFA_SCORE >= 11, "high", "moderate")))

comb <- comb %>% mutate(cancertype = ifelse(GIMAL == "Yes", "GI", ifelse(TRUELYMPHOMA == "Yes", "LYMPHOMA", ifelse(LEUKEMIA == "Yes", "LEUKEMIA", ifelse(OTHERHEMMAL == "Yes", "OTHER HEMATOLOGIC", ifelse(OTHERMAL == "Yes", "OTHER", ifelse(ORALMAL == "Yes", "ORAL", ifelse(RESPMAL == "Yes", "RESPIRATORY", ifelse(CONNMAL == "Yes", "CONNECTIVE TISSUE", ifelse(GUMAL == "Yes", "GU", NA ))))))))))

comb <- comb %>% mutate(cancertype2 = ifelse(GIMAL == "Yes", "GI", ifelse(TRUELYMPHOMA == "Yes", "LYMPHOMA", ifelse(LEUKEMIA == "Yes", "LEUKEMIA", ifelse(OTHERHEMMAL == "Yes", "OTHER HEMATOLOGIC", ifelse(OTHERMAL == "Yes", "OTHER", ifelse(ORALMAL == "Yes", "ORAL", ifelse(RESPMAL == "Yes", "RESPIRATORY", ifelse(CONNMAL == "Yes", "CONNECTIVE TISSUE", ifelse(GUMAL == "Yes", "GU", "No cancer" ))))))))))


comb <- comb %>% mutate(typeonc = ifelse(GIMAL == "Yes", "GI", ifelse(ORALMAL == "Yes", "ORAL", ifelse(RESPMAL == "Yes", "RESPIRATORY", ifelse(CONNMAL == "Yes", "CONNECTIVE TISSUE", ifelse(GUMAL == "Yes", "GU", ifelse(OTHERMAL == "Yes", "OTHER", NA )))))))

comb <- comb %>% mutate(typehem = ifelse(TRUELYMPHOMA == "Yes", "LYMPHOMA", ifelse(LEUKEMIA == "Yes", "LEUKEMIA", ifelse(OTHERHEMMAL == "Yes", "OTHER", NA))))

comb <- comb %>%  mutate(hem_onc = ifelse(hem.flg == "1", "Hematologic", ifelse (onc.flg == "1", "Solid", "No cancer")))

comb <- comb %>% mutate(METASTATIC_CANCER = ifelse(onc.flg == "1" & METASTATIC_CANCER==1, 1, 0))

comb$LYMPHOMA<- as.factor(comb$LYMPHOMA)
comb$SOLID_TUMOR<- as.factor(comb$SOLID_TUMOR)
comb$m28.flg<-as.factor(comb$m28.flg)
comb$m1y.flg<-as.factor(comb$m1y.flg)
comb$METASTATIC_CANCER<- as.factor(comb$METASTATIC_CANCER)
comb$mal.flg<-as.factor(comb$mal.flg)
comb$RRT<-as.factor(comb$RRT)
comb$DNR_ADMISSION<-as.factor(comb$DNR_ADMISSION)
comb$CMO_ADMISSION<-as.factor(comb$CMO_ADMISSION)
comb$vaso.flg<-as.factor(comb$vaso.flg)
comb$vent.flg<-as.factor(comb$vent.flg)

comb<-merge(x=comb,y=angus)
comb$SEPSIS<-as.factor(comb$SEPSIS)

cancer <- comb
cancer = cancer[which(as.character(cancer[,"mal.flg"])=="1"),]
onc= cancer[which(as.character(cancer[,"onc.flg"])=="1"),]
hem= cancer[which(as.character(cancer[,"hem.flg"])=="1"),]
noncancer=comb[which(as.character(comb[,"mal.flg"])=="0"),]
```

```{r echo=FALSE}
set_theme(theme_light())

comb$hem_onc <- factor(comb$hem_onc, 
        levels = c("Hematologic", "Solid", "No cancer"),
        labels = c("Hematologic malignancy", "Solid cancer", "No cancer")        
        )
tiff(filename = "Rplot%03d.tif",
     width = 800, height = 480, units = "px", pointsize = 18,
     compression = c("none", "rle", "lzw", "jpeg", "zip", "lzw+p", "zip+p"),
     bg = "white", res = NA, family = "", restoreConsole = TRUE,
     type = c("windows", "cairo"))
ggplot(comb,aes(x = GROUP, fill = hem_onc), geom.outline.size = 0, geom.label.size = 4, geom.outline.color=1)+  geom_bar(position = "fill", show.legend = T)+ labs(title="Cancer Patients as a Proportion of Overall Admissions", x="Year of admission", y="Proportion of patients")
```

```{r}
cancer$cancertype2 <- factor(cancer$cancertype2, 
        levels = c("CONNECTIVE TISSUE", "GI", "GU", "ORAL", "RESPIRATORY", "OTHER", "LEUKEMIA", "LYMPHOMA", "OTHER HEMATOLOGIC"),
        labels = c("Connective tissue", "Gastrointestinal", "Genitourinary", "Oral", "Respiratory", "Other solid cancer", "Leukemia", "Lymphoma", "Other hematologic malignancy")        
        )

comb$cancertype2 <- factor(comb$cancertype2, 
        levels = c("CONNECTIVE TISSUE", "GI", "GU", "ORAL", "RESPIRATORY", "OTHER", "LEUKEMIA", "LYMPHOMA", "OTHER HEMATOLOGIC", "No cancer"),
        labels = c("Connective tissue", "Gastrointestinal", "Genitourinary", "Oral", "Respiratory", "Other solid cancer", "Leukemia", "Lymphoma", "Other hematologic malignancy", "No cancer")        
        )

tiff(filename = "Rplot%03d.tif",
     width = 900, height = 480, units = "px", pointsize = 12,
     compression = c("none", "rle", "lzw", "jpeg", "zip", "lzw+p", "zip+p"),
     bg = "white", res = NA, family = "", restoreConsole = TRUE,
     type = c("windows", "cairo"))
ggplot(cancer,aes(x = GROUP, fill = cancertype2))+  geom_bar(position = "fill", show.legend = T)+ labs(title="Trends in admission of cancer patients by subtype", x="Year of admission", y="Proportion of patients")

```

```{r}
set_theme(geom.outline.color = "antiquewhite4", 
             geom.outline.size = 5, 
             geom.label.size = 4.5,
             geom.label.color = "grey50",
              panel.gridcol.x =  "white",
             title.color = "black", 
             title.size = 1.5, 
             axis.angle.x = 0, 
             axis.textcolor = "black", 
             base = theme_bw() )

```



```{r, message= FALSE}
plot_prop_by_level(comb, "GROUP", "m28.flg", factor.var2="hem_onc", ylab= "28-Days Mortality")
plot_prop_by_level(comb, "GROUP", "m1y.flg", factor.var2="hem_onc", ylab= "1-Year Mortality")


plot_prop_by_level(comb, "GROUP", "APSIII_SCORE",factor.var2="mal.flg", ylab="APACHE III Score")

plot_prop_by_level(comb, "GROUP", "OASIS_SCORE",factor.var2="mal.flg", ylab="OASIS Score")

```

#Curde odds ratios mortality
```{r}
table(comb$hem_onc, comb$m28.flg)
oddsratio(comb$hem_onc, comb$m1y.flg)
oddsratio(comb$SOLID_TUMOR, comb$m1y.flg)
oddsratio(comb$LYMPHOMA, comb$m1y.flg)
oddsratio(comb$METASTATIC_CANCER, comb$m1y.flg)
oddsratio(comb$GROUP, comb$m1y.flg)
```



#Crude odds ratio 28-day mortality in the presence and absence of a malignancy

```{r, echo = FALSE}
oddsratio(comb$hem.flg, comb$m1y.flg)
```

# Prognosis by SOFA scores

```{r}
plot_prop_by_level(comb, "cancertype2", "m28.flg",factor.var2="sofa.cut", ylab="Proportion dying within 28 days")
plot_prop_by_level(comb, "cancertype2", "m1y.flg",factor.var2="sofa.cut", ylab="Proportion dying within 1 year")
table(comb$sofa.cut, comb$cancertype)

```

# 28d/ 1yr mortality

```{r}
tiff(filename = "Rplot%03d.tif",
     width = 1000, height = 480, units = "px", pointsize = 12,
     compression = c("none", "rle", "lzw", "jpeg", "zip", "lzw+p", "zip+p"),
     bg = "white", res = NA, family = "", restoreConsole = TRUE,
     type = c("windows", "cairo"))
plot_prop_by_level(comb, "cancertype2", "m28.flg",factor.var2="GROUP", ylab="Proportion dying within 28 days")
par(mfrow = c(1,1))

tiff(filename = "Rplot%03d.tif",
     width = 1000, height = 480, units = "px", pointsize = 12,
     compression = c("none", "rle", "lzw", "jpeg", "zip", "lzw+p", "zip+p"),
     bg = "white", res = NA, family = "", restoreConsole = TRUE,
     type = c("windows", "cairo"))
plot_prop_by_level(comb, "cancertype2", "m1y.flg",factor.var2="GROUP", ylab="Proportion dying within 1 year")
par(mfrow = c(1,1))
```


# 28d/ 1yr mortality by cancer type
```{r}
plot_prop_by_level(comb, "typeonc", "m28.flg",factor.var2="GROUP", ylab="Proportion dying within 28 days")
plot_prop_by_level(comb, "typeonc", "m1y.flg",factor.var2="GROUP", ylab="Proportion dying within 1 year")


table(comb$typeonc, comb$m28.flg)
```
# 28d/ 1yr mortality by hematologic type
```{r}
plot_prop_by_level(comb, "typehem", "m28.flg",factor.var2="GROUP", ylab="Proportion dying within 28 days")
plot_prop_by_level(comb, "typehem", "m1y.flg",factor.var2="GROUP", ylab="Proportion dying within 1 year")
```


## Table 1
#Overview of patient characteristics stratified by the presence of a hematological and oncological malignancy. 
Yes:No = only hematologic malignancy
No:Yes = only solid tumor
Yes:Yes = both solid and hematologic malignancy

```{r}
CreateTableOne(vars=c("ADMISSION_TYPE","SEPSIS", "CMO_ADMISSION","DNR_ADMISSION","METASTATIC_CANCER","AGE_ADMISSION", "race2", "LOS_ICU", "LOS_HOSPITAL", "vent.flg", "vaso.flg", "RRT", "ELIXHAUSER_SID30","SOFA_SCORE","APSIII_SCORE","m28.flg","m1y.flg" ),strata=c("hem.flg", "onc.flg") ,data= comb,test=F) %>% print(
  printToggle      = FALSE,
  showAllLevels    = TRUE,
  cramVars         = "kon"
) %>% 
{data.frame(
  variable_name             = gsub(" ", "&nbsp;", rownames(.), fixed = TRUE), ., 
  row.names        = NULL, 
  check.names      = FALSE, 
  stringsAsFactors = FALSE)} %>% 
knitr::kable()
```

#Alternative: Stratified by year of admission- CANCER PATIENTS ONLY!!!
```{r}
CreateTableOne(vars=c("AGE_ADMISSION","SEPSIS","DNR_ADMISSION","race2","vaso.flg","vent.flg", "typeonc", "typehem","METASTATIC_CANCER","RRT", "ELIXHAUSER_SID30" ,"SOFA_SCORE","APSIII_SCORE","OASIS_SCORE", "LOS_ICU", "LOS_HOSPITAL", "m28.flg","m1y.flg") ,strata="GROUP",data=cancer,test=F) %>% print(
  printToggle      = FALSE,
  showAllLevels    = TRUE,
  cramVars         = "kon"
) %>% 
{data.frame(
  variable_name             = gsub(" ", "&nbsp;", rownames(.), fixed = TRUE), ., 
  row.names        = NULL, 
  check.names      = FALSE, 
  stringsAsFactors = FALSE)} %>% 
knitr::kable()
```


#Odds ratio of 28d (fig.1) and 1-year mortality (fig.2) by year of admission. 2002=baseline

```{r, echo= FALSE}
plot_OR_by_level(comb, "hem_onc", "m28.flg",factor.var2="GROUP", include.ref.group.effect = TRUE)
plot_OR_by_level(comb, "hem_onc", "m1y.flg",factor.var2="GROUP", include.ref.group.effect = TRUE)
```

#Trends in mortality between 2002-2011 for patients with solid malignancies

```{r, echo = FALSE}
plot_prop_by_level(comb, "onc.flg", "m1y.flg",factor.var2="GROUP", ylab="1-year mortality")
plot_prop_by_level(comb, "onc.flg", "m28.flg",factor.var2="GROUP", ylab="28-day mortality")
```

#Odds ratio of 28d (fig.1) and 1-year mortality (fig.2) by year of admission

```{r, echo= FALSE}
plot_OR_by_level(comb, "onc.flg", "m28.flg",factor.var2="GROUP", ylab="28-day mortality")
plot_OR_by_level(comb, "onc.flg", "m1y.flg",factor.var2="GROUP", ylab="1-year mortality")
```

#Trends in mortality between 2002-2011 for patients with hematologic malignancies
```{r, echo= FALSE}
plot_prop_by_level(comb, "hem.flg", "m1y.flg",factor.var2="GROUP", ylab="1-year mortality")
plot_prop_by_level(comb, "hem.flg", "m28.flg",factor.var2="GROUP", ylab="28-day mortality")
plot_prop_by_level(comb, "cancertype", "m28.flg",factor.var2="GROUP", ylab="28-day mortality")
```

#Odds ratio of 28d (fig.1) and 1-year mortality (fig.2) by year of admission

```{r, echo= FALSE}
plot_OR_by_level(comb, "hem.flg", "m28.flg",factor.var2="GROUP")
plot_OR_by_level(comb, "hem.flg", "m1y.flg",factor.var2="GROUP")
```

# Logistic regression model, outcome=28day mortality 

```{r, echo = FALSE}
m28.glm <- glm(m28.flg ~ onc.flg + GROUP + vent.flg+ vaso.flg+ APSIII_SCORE + AGE_ADMISSION + race2 +  ELIXHAUSER_SID30 + DNR_ADMISSION+ ICU_TYPE+ GENDER, data=comb, family="binomial")
exp(m28.glm$coefficients)
exp(confint(m28.glm))
sjp.glm(m28.glm, show.values = TRUE, vline.type = 1, grid.breaks = 100)

```

# Logistic regression model, outcome=28day mortality , cancer patients only

```{r, echo = FALSE}
m28c.glm <- glm(m28.flg ~  GROUP + vent.flg+ AGE_ADMISSION+vaso.flg+ APSIII_SCORE + race2 +  ELIXHAUSER_SID30 + DNR_ADMISSION+ ICU_TYPE+ GENDER+typeonc, data=onc, family="binomial")
AIC(m28c.glm)
exp(m28c.glm$coefficients)
exp(confint(m28c.glm))
plot_model(m28c.glm, show.values = TRUE,  title = "28-day Mortality Solid Malignancies", sort.est = T, axis.lim = c(0.3,5))

m28h.glm <- glm(m28.flg ~  GROUP + vent.flg+ vaso.flg+ AGE_ADMISSION+ APSIII_SCORE + race2 +  ELIXHAUSER_SID30 + DNR_ADMISSION+ ICU_TYPE+ GENDER+typehem, data=hem, family="binomial")
(exp(m28h.glm$coefficients))
round(exp(confint(m28h.glm)), digits = 2)
plot_model(m28h.glm, show.values = TRUE, title = "28-day Mortality Hematologic Malignancies", show.p = T, sort.est = T, axis.lim = c(0.02,20))

```


# Logistic regression model, outcome=1 year mortality 


```{r, echo = FALSE}
comb$m1y.flg<- as.factor(comb$m1y.flg)
m1y.glm <- glm(m1y.flg ~ mal.flg +GROUP + vent.flg+ vaso.flg+ APSIII_SCORE + AGE_ADMISSION + race2 +  ELIXHAUSER_SID30 + DNR_ADMISSION+ ICU_TYPE+ GENDER,data=comb, family="binomial")
summary(m1y.glm)
exp(confint(m1y.glm))
sjp.glm(m1y.glm, show.values = TRUE, vline.type = 1)
```

# Logistic regression model, outcome=1 year mortality , cancer patients only


```{r, echo = FALSE}
comb$m1y.flg<- as.factor(comb$m1y.flg)
m1yh.glm <- glm(m1y.flg ~  GROUP + vent.flg+ AGE_ADMISSION+vaso.flg+ APSIII_SCORE + race2 +  ELIXHAUSER_SID30 + DNR_ADMISSION+ ICU_TYPE+ GENDER+ typehem,data=hem, family="binomial")
summary.glm(m1yh.glm)
exp(confint(m1yh.glm))
plot_model(m1yh.glm, show.values = TRUE, vline.type = 1, title = "1-year Mortality Hematologic Malignancies", show.p = T, sort.est = T,  axis.lim = c(0.05, 10))

m1ys.glm <- glm(m1y.flg ~  GROUP + vent.flg+ AGE_ADMISSION+ vaso.flg+ APSIII_SCORE + race2 +  ELIXHAUSER_SID30 + DNR_ADMISSION+ ICU_TYPE+ GENDER+ typeonc,data=onc, family="binomial")
summary.glm(m1ys.glm)
exp(confint(m1ys.glm))
plot_model(m1ys.glm, show.values = TRUE, vline.type = 1, title = "1-year Mortality Solid Malignancies", show.p = T, sort.est = T, axis.lim = c(0.1,10))
```


```{r}
table(comb$cancertype2)
subset=comb[comb$METASTATIC_CANCER==1,]
m28.glm <- glm(m28.flg ~ GROUP + vent.flg+ vaso.flg+ APSIII_SCORE + AGE_ADMISSION + race2 +  ELIXHAUSER_SID30 + DNR_ADMISSION+ ICU_TYPE+ GENDER, data=subset, family="binomial")
exp(m28.glm$coefficients)
exp(confint(m28.glm))
m1ysub.glm <- glm(m1y.flg ~ GROUP + vent.flg+ vaso.flg+ APSIII_SCORE + AGE_ADMISSION + race2 +  ELIXHAUSER_SID30 + DNR_ADMISSION+ ICU_TYPE+ GENDER, data=subset, family="binomial")
exp(m1ysub.glm$coefficients)
exp(confint(m1ysub.glm))
```




